%-------------------------
% Resume in Latex
% Original Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
% !TEX root = /main.tex

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Alexander C. Kim} \\ \vspace{1pt}
    \small 321-594-8873 $|$ \href{mailto:x@x.com}{{alexk2k05@gmail.com}} $|$ 
    \href{https://linkedin.com/in/alexander-c-kim}{{linkedin.com/in/alexander-c-kim}} $|$
    \href{https://github.com/alex-chae-kim}{{github.com/alex-chae-kim}}
\end{center}


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Science in Computer Science, Minor in Mathematics}{May 2027}
      {University of Florida - Honors Program - Herbert Wertheim College of Engineering}{GPA: 3.93/4.0}
      \begin{itemize}[leftmargin=0in, label={}]
        \small{\item{
        \textbf{Relevant Coursework}{: Discrete Structures, Computer Organization, Computational Linear Algebra, Data Structures and Algorithms, Software Engineering, Sets and Logic} \\
        }}
    \end{itemize}
  \resumeSubHeadingListEnd

%-----------TECH SKILLS-----------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, C\#, Python, Javascript} \\
     \textbf{Libraries/Frameworks}{: React, Express.js, Passport.js, Socket.io, EnTT, ImGui} \\
     \textbf{Technologies/Tools}{: Unity, Git, MongoDB, Vercel, Render, Matlab, Meshmixer} \\

    }}
 \end{itemize}

 %-----------Involvement-----------
 \section{\textbf{Leadership}}
 \resumeSubHeadingListStart
   \resumeProjectHeading
       {\textbf{Director of Recruitment} $|$ {Dream Team Engineering}}{May 2024 -- Present}
       \resumeItemListStart
         \resumeItem{Organized applications, scheduled interviews, and answered questions for over 350 applicants.}
         \resumeItem{Communicated effectively with over 40 captains and executive board members throughout the recruitment process.}
         \resumeItem{Planned 8 social, informational, and professional events which increased applications by over 40\%.}
       \resumeItemListEnd
 \resumeSubHeadingListEnd
 
%-----------EXPERIENCE-----------
\section{\textbf{Project Experience}}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {Infantile IV Procedure Simulator}{September 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Captained a team of 9 to develop a mixed-reality simulator with Unity and SMMARTS SDK, improving pediatric procedural training.}
        \resumeItem{Collaborated with UF engineers and physicians to ensure simulation accuracy and calibration of physical instruments.}
        \resumeItem{Implemented data handling systems for formatting and exporting procedural data, enabling performance tracking for trainees.}
        \resumeItem{Presented trainer at ACS Surgeons  \& Engineers Summit (2025) to 130 international attendees.}
      \resumeItemListEnd

      \resumeProjectHeading
      {Virtual Reality MRI}{January 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Led a 3 person team to develop a VR MRI simulation in Unity for Meta Quest, designed to reduce patient anxiety through immersive education.}
        \resumeItem{Built a customizable object-oriented framework supporting 350,000+ MRI scan combinations, enabling flexible research configurations.}
        \resumeItem{Developed player locomotion, dynamic repositioning, and interaction mechanics for realistic clinical simulation.}
      \resumeItemListEnd

      \resumeProjectHeading
      {CloudStep Engine}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Co-developed and implemented core engine architecture in C++ with EnTT for scalable entity-component systems.}
        \resumeItem{Built a custom 2D physics system and wrote unit and integration tests for reliability.}
        \resumeItem{Integrated an ImGui powered editor interface, accelerating debugging and workflow efficiency by enabling real-time component editing.}
        \resumeItem{Applied Git best practices for collaborative development and maintainability.}
      \resumeItemListEnd

      \resumeProjectHeading
      {GatorTrade}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Implemented secure Google OAuth2.0 authentication with Passport.js.}
        \resumeItem{Developed robust Express.js backend with optimized MongoDB queries for CRUD operations, improving listing retrieval performance for users.}
        \resumeItem{Integrated real-time messaging with Socket.io, enabling fast, reliable communication between buyers and sellers.}
        \resumeItem{Conducted pre-deployment UX testing, iterative bug fixes, and deployed via Vercel and Render for scalable hosting.}
      \resumeItemListEnd
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeProjectHeading
      {Your Anime Link}{Nov. 2024}
      \resumeItemListStart
        \resumeItem{Created an anime recommending tool using C++ and Python for csv formatting.}
        \resumeItem{Developed an algorithm that recommended anime with 90\% satisfaction.}
        \resumeItem{Achieved consistent 1 second runtime searching over 24k anime with over 200k parameters.}
    \resumeItemListEnd

    \resumeProjectHeading
      {GatORGanizer}{Mar. 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Harnessed ChatGPT 3.5 and the Instaloader API to summarize UF organization announcements.}
        \resumeItem{Utilized the Google Calendar API to incorporate club events into users' calendars.}
        \resumeItem{Stored club data in a SQL database.}
      \resumeItemListEnd

      \resumeProjectHeading
      {Tabbed In}{Oct. 2023}
      \resumeItemListStart
        \resumeItem{Developed an educational 2D game for children about the human body.}
        \resumeItem{Worked as the lead developer on a team of 4 to create the game using Unity from scratch in 24 hours.}
        \resumeItem{Achieved 1st place among over 80 participants.}
    \resumeItemListEnd

    \resumeProjectHeading
      {Jigsaw Jutsu}{Jan. 2023 -- Feb 2023}
      \resumeItemListStart
        \resumeItem{Developed a first-person 3D game using Unity about throwing puzzle pieces like ninja stars.}
        \resumeItem{Wrote all scripts required for game functionality as the only programmer on the team.}
        \resumeItem{Achieved 1st place at a statewide competition attended by over 2k students.}
    \resumeItemListEnd

    \resumeProjectHeading
      {Turtle All The Way Up}{Jan. 2023 -- Feb 2023}
      \resumeItemListStart
        \resumeItem{Developed a first-person 3D game using Unity about throwing puzzle pieces like ninja stars.}
        \resumeItem{Wrote all scripts required for game functionality as the only programmer on the team.}
        \resumeItem{Achieved 1st place at a statewide competition attended by over 2k students.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%
%      \resumeProjectHeading
%         {\textbf{Undergraduate Research Assistant} $|$ \emph{University of Florida Department of Chemistry}}{Jan 2024 -- May 2024}
%          \resumeItemListStart
%            \resumeItem{Investigated the kinetics and specificity of SARS-CoV-2 Nsp15 endonuclease}
%            \resumeItem{Learned essential wet lab skills like gel electrophoresis, enzyme assay preparation, and scientific note-taking}
%            \resumeItem{Collaborated with two other assistant researchers to triple productivity}
%            \resumeItem{Presented research at the Spring Undergraduate Research Symposium}
%          \resumeItemListEnd

%-----------CERTS-----------
\section{\textbf{Certifications}}
\begin{itemize}[leftmargin=0in, label={}, itemsep=0pt, parsep=0pt]
    \small{
        \item{
            \textbf{Introduction to Concurrency with C++ (CodeSignal)} 
            \hfill {June 2025} \\
        }
    }
\end{itemize}

%-------------------------------------------
\end{document}
